Supplementary figures

### 2015-07-16 Manuscript/supplementary.tex
Updates to supp figures

\begin{figure}
\includegraphics[scale=0.5]{figure/supplement_1.pdf}
\caption{The proportion of simulations resulting in endemic disease dynamics (persistence of both susceptible and infectious hosts) as a function of disease-induced mortality ($\nu$), and the probability of direct transmission ($\delta$).  Panel columns show low (0.3, a, d), medium (1.0, b, e), and high (3.2, c, f) pathogen longevities, while rows show high quality (ranging from 0.76 to 1.77, a - c) and low quality (ranging from 0.23 to 1.24, d - f) patch quality distributions.  Darker shading corresponds to more frequent endemic dynamics.  The white region above the endemic region generally corresponds to pandemic dynamics (no susceptible host populations persist), while the region below the endemic region corresponds to disease-free dynamics.}
\label{endemic}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.5]{figure/supplement_1.pdf}
\caption{Median total susceptible population size as a function of infectious survival ($\nu$), and the probability of direct transmission ($\delta$).  Panel columns show low (0.3, a, d), medium (1.0, b, e), and high (3.2, c, f) pathogen longevities, while rows show low quality (ranging from 0.23 to 1.24, a - c) and high quality (ranging from 0.76 to 1.77, d - f) patch quality distributions.  Darker shading corresponds to larger population sizes, while white indicates that no susceptible host populations persist (i.e. all host populations become infected).}
\label{endemic}
\end{figure}
